Stochastic Multiple Output Gaussian Processes

### 2014-03-06 paper/experiments.tex
paper

\section{Toy Experiments}
The first toy experiment uses two identical outputs which are noisy version of the same version plus some noise: $y_1(x) = sin(x) + \epsilon$ and $y_2(x) = sin(x) + \epsilon$, $\epsilon \sim \Normal(0,0.01)$.
In this case the shared function $g(x)$ is $sin(x)$ and the independent processes $h_1(x)$ and $h_2(x)$ are just white noises.
Each output has missing values in one region of the input space.
The predictive distributions of the multiple-gp model compared to that of independent gps are shown in \ref{fig4}.

\noindent The second toy experiment uses similar setting as the first one, except that now $y_1(x) = sin(x) + \epsilon$ and $y_2(x) = -sin(x) + \epsilon$. 
In this case the shared function is still $g(x) = sin(x)$, but the weights should be opposite i.e. $w_1 = 1$ and $w_2 = 1$.
The learning procedure was indeed able to recovered this relation and learned that $w_1 = 1.2$ and $w_2 = -1.3$.
The predictive distributions are shown in \ref{fig5}.

\begin{figure*}
\centering
\begin{tabular}{cc}
\includegraphics[scale=0.5]{figures/ssvi-y1.eps} &
\includegraphics[scale=0.5]{figures/ssvi-svi1.eps} \\
\includegraphics[scale=0.5]{figures/ssvi-y2.eps} &
\includegraphics[scale=0.5]{figures/ssvi-svi2.eps} \\
\multicolumn{2}{c}{\includegraphics[scale=0.5]{figures/ssvi-y1byg.eps} }
\end{tabular}
\label{fig4}
\caption{Predictive distributions of the multipe-output gps (left column) and independent gps (right column) for the first toy example. The predictive distribution by $g(x)$ for $y_1(x)$ is shown in the bottom figure.}
\end{figure*}

\begin{figure*}
\centering
\begin{tabular}{cc}
\includegraphics[scale=0.5]{figures/ssvi2-y1.eps} &
\includegraphics[scale=0.5]{figures/ssvi2-svi1.eps} \\
\includegraphics[scale=0.5]{figures/ssvi2-y2.eps} &
\includegraphics[scale=0.5]{figures/ssvi2-svi2.eps} \\
\multicolumn{2}{c}{\includegraphics[scale=0.5]{figures/ssvi-y1byg.eps} }
\end{tabular}
\label{fig5}
\caption{Predictive distributions of the multipe-output gps (left column) and independent gps (right column) for the second toy experiment. The predictive distribution by $g(x)$ for $y_1(x)$ is shown in the bottom figure.}
\end{figure*}

>>>>

We perform three sets of experiments to evaluate the model and the stochastic variational inference proposed. 
First, we use a toy problem to demonstrate the effectiveness of the proposed method in learning the model parameters.
Second, we assess the predictive accuracy of the model on two medium-sized datasets and compare with existing multiple output models.
In the final experiments, we evaluate the model on large-scale learning with multiple tasks.

\subsection{TOY PROBLEM}
In this toy problem we use two related outputs generated from the same latent function $sin(x)$ but are corrupted by independent noises: $y_1(x) = sin(x) + \epsilon$ and $y_2(x) = -sin(x) + \epsilon$, $\epsilon \sim \Normal(0,0.01)$.
Each output has missing values in one region of the input space.
% Say that this is from a single gpsvi
The predictive distributions of the model compared to that of independent gps are shown in \ref{fig5}.

\begin{figure*}
\centering
\begin{tabular}{cc}
\includegraphics[scale=0.5]{figures/ssvi2-y1.eps} &
\includegraphics[scale=0.5]{figures/ssvi2-svi1.eps} \\
\includegraphics[scale=0.5]{figures/ssvi2-y2.eps} &
\includegraphics[scale=0.5]{figures/ssvi2-svi2.eps} \\
\end{tabular}
\label{fig5}
\caption{Predictive distributions of the multioutput gps (left column) and independent gps (right column) for the second toy experiment. The predictive distribution by $g(x)$ for $y_1(x)$ is shown in the bottom figure.}
\end{figure*}

\subsection{EVALUATION OF THE PREDICTIVE ACCURACY}
\subsubsection{Foregin Exchange Rate Prediction}
\subsubsection{Weather Data Prediction}

\subsection{LARGE-SCALE EXPERIMENTS}
\subsubsection{Robort Arms}
\subsubsection{Foreign Exchange Rate Prediction}

### 2014-03-06 paper/paper.tex
paper

\section{DISCUSSION}
\input{discussion}

\subsubsection{Figures}

All artwork must be centered, neat, clean, and legible. Figure number
and caption always appear below the figure.  Leave 2 line spaces
between the figure and the caption. The figure caption is initial caps
and each figure numbered consecutively.

Make sure that the figure caption does not get separated from the
figure. Leave extra white space at the bottom of the page rather than
splitting the figure and figure caption.
\begin{figure}[h]
\vspace{1in}
\caption{Sample Figure Caption}
\end{figure}

\subsubsection{Tables}

\begin{table}[h]
\caption{Sample Table Title}
\label{sample-table}
\begin{center}
\begin{tabular}{ll}
\multicolumn{1}{c}{\bf PART}  &\multicolumn{1}{c}{\bf DESCRIPTION} \\
\hline \\
Dendrite         &Input terminal \\
Axon             &Output terminal \\
Soma             &Cell body (contains cell nucleus) \\
\end{tabular}
\end{center}
\end{table}

\newpage
\section{APPENDIX}
Perhaps this should go to a supplementary material.
\input{appendix}

>>>>

\section{DISCUSSION}
\input{discussion}
\newpage
\section{APPENDIX}
Perhaps this should go to a supplementary material.
\input{appendix}
